\protect Connecting every bit of knowledge: \\ The Structure of Wikipedia's first link network

### 2016-02-22 writeup/wikipedia-network.tex
first link justfication added

The authors of a Wikipedia article choose where and whether to include a 
reference to another Wikipedia article
in the HTML markup.
For example, the authors of the 
\href{https://en.wikipedia.org/wiki/Train}{``Train''}
article chose
``Rail Transport,'' ``Cargo,'' and ``Passengers'' 
as pertinent articles to reference in describing trains
\cite{wiki_train}
.
Here we focus on the first hyperlink to another Wikipedia article, which 
marks the earliest moment in the body text where the authors
chose to connect the information discussed to that of another article.
By following the first hyperlink to another article in the English edition of
Wikipedia as of November, 2014, we connect the ideas in one article to those in another, ultimately forming a directed network: 
{\it Wikipedia's First Link Network} (FLN).

>>>>

The authors of a Wikipedia article choose where and whether to include a 
reference to another Wikipedia article
in the HTML markup.
For example, the authors of 
\href{https://en.wikipedia.org/wiki/Train}{``Train''}
chose
``Amtrak's Acela Express,'' ``steam,'' and ``head-end power'' 
among others as relevant articles to reference in describing ``Train''
\cite{wiki_train}
.
By focusing our attention on the main body of an article---excluding
elements in the side bars and headings---we capture the introduction to the topic.
The first link marks the earliest moment in a topic's introduction where the 
authors choose to directly reference another article. 
While the many links in an article may reference relevant details to a topic, 
the first link is an association within the introductory 
description. While 
``Amtrak's Acela Express,'' ``steam,'' and ``head-end power'' 
are links detailing particulars, the first link, ``rail transport,''
is the topic the authors associate with ``Train'' in the introduction. 
Collectively, the first links provide a pragmatic and interpretable 
means to connect each article to another.

By following the first hyperlink to another article in the English edition of
Wikipedia as of November, 2014, we connect the ideas in one article to those in another, ultimately forming a directed network: 
{\it Wikipedia's First Link Network} (FLN).
